Mechanical and luminescence-based detection of dipolar-interactions between spins in diamond

### 2020-12-04 Talks/Défaut 2020/presentation.tex
totto

\title{Mechanical and relaxation-based detection of dipolar-interactions between spins in diamond}
\author{Clément Pellet-Mary\\ Laboratoire de physique de l'ENS\\ \textit{ENS, Paris}}
\date\today

@@

\begin{frame}{Two experiments around cross-relaxations in diamond}

@@

\tableofcontents

@@

\includegraphics[scale=.25]{projection_4_classes}

@@

\begin{frame}{Exemple of C.R. : scan along the [111]}
\includegraphics[scale=.30]{CR_111}\footfullcite{armstrong_nvnv_2010}

@@

\includegraphics[scale=.3]{Motivations}\footfullcite{tallaire2020high}

@@

\includegraphics[scale=.45]{Scan_100_brut}

@@

\begin{frame}{Comparison between CR and EPR}

@@

\item CR experiments are much simpler to setup (low $B$, no microwave)

@@

\item NV centers produce a calibration for $B$ $\to$ Better precision on the ZFS measurement
\item Potential for polarization transfer
\item Requires a high NV concentration and quickly becomes unreadable on non-[100] directions.

@@

\begin{frame}{Experimental proofs of NV-NV CR}
\includegraphics[scale=.28]{NV-NV_0}

@@

\includegraphics[scale=.3]{Trap_3}%And how do we measure this rotation ? well, since we have to send a laser on the diamond to polarise the NV centers..." "We do not observe a clear reflection of the laser, instead we observe a speckle pattern, which is produced by the many interferences on the rough surface of the diamond" "Whenever the diamond moves, the speckle pattern will either shift or change its shape..."

@@

\includegraphics[scale=.08]{CRmeca_121_mieux}

@@

\includegraphics[scale=.23]{Explication_torque_alalouche}

>>>>

\title{Mechanical and luminescence-based detection of dipolar-interactions between spins in diamond}
\author{Clément Pellet-Mary\\ Laboratoire de physique de l'ENS\\ \textit{ENS, Paris}}
\date\today

@@

@@

@@

\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.25]{projection_4_classes_0}
    \onslide<2>\includegraphics[scale=.25]{projection_4_classes_1}
    \end{overprint}
\end{figure}

@@

\begin{frame}{Exemple of Cross-Relaxation NV-P1}
\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.30]{CR_111_0}\footfullcite{armstrong_nvnv_2010}
    \onslide<2>\includegraphics[scale=.30]{CR_111_05}
    \onslide<3>\includegraphics[scale=.30]{CR_111_1}
    \onslide<4>\includegraphics[scale=.30]{CR_111_2}
    \end{overprint}
\end{figure}

@@

\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.30]{Motivations_0}
    \onslide<2>\includegraphics[scale=.30]{Motivations_1}\footfullcite{tallaire2020high}
    \onslide<3>\includegraphics[scale=.30]{Motivations_2}
    \onslide<4>\includegraphics[scale=.30]{Motivations_3}
    \end{overprint}
\end{figure}

@@

\begin{figure}
    \begin{overprint}
    \onslide<1>\centering\includegraphics[scale=.45]{Scan_100_brut_0}
    \onslide<2>\centering\includegraphics[scale=.45]{Scan_100_brut_1}
    \onslide<3>\centering\includegraphics[scale=.45]{Scan_100_brut_2}
    \end{overprint}
\end{figure}

@@

\begin{frame}{Comparison between cross-relaxation and EPR}
\pause
Upsides :

@@

\item CR experiments are much simpler to setup (low $\vec B$, no microwave)
\pause

@@

\pause
\item NV centers produce a calibration for $\vec B$ $\to$ Better precision on the ZFS measurement
\pause
\item Potential for hyperpolarization of new spins
\pause
Downsides :
\item Requires a high NV concentration
\pause
\item Loss of contrast in non-[100] directions

@@

\begin{frame}{Experimental proofs of NV-NV cross-relaxations}
\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.28]{NV-NV_0}
    \onslide<2>\includegraphics[scale=.28]{NV-NV_05}
    \onslide<3>\includegraphics[scale=.28]{NV-NV_1}
    \onslide<4>\includegraphics[scale=.28]{NV-NV_2}
    \onslide<5>\includegraphics[scale=.28]{NV-NV_3}
    \end{overprint}
\end{figure}

@@

\includegraphics[scale=.085]{Trap_3}%And how do we measure this rotation ? well, since we have to send a laser on the diamond to polarise the NV centers..." "We do not observe a clear reflection of the laser, instead we observe a speckle pattern, which is produced by the many interferences on the rough surface of the diamond" "Whenever the diamond moves, the speckle pattern will either shift or change its shape..."

@@

\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.08]{CRmeca_121_mieux_0}
    \onslide<2>\includegraphics[scale=.08]{CRmeca_121_mieux_1}
    \onslide<3>\includegraphics[scale=.08]{CRmeca_121_mieux_2}
    \end{overprint}
\end{figure}

@@

\begin{figure}
    \begin{overprint}
    \onslide<1>\includegraphics[scale=.23]{Explication_torque_alalouche_0}
    \onslide<2>\includegraphics[scale=.23]{Explication_torque_alalouche_1}
    \onslide<3>\includegraphics[scale=.23]{Explication_torque_alalouche_2}
    \onslide<4>\includegraphics[scale=.23]{Explication_torque_alalouche_3}
    \onslide<5>\includegraphics[scale=.23]{Explication_torque_alalouche_4}
    \onslide<6>\includegraphics[scale=.23]{Explication_torque_alalouche_5}
    \end{overprint}
\end{figure}
